Title

### 2023-10-06 paper/paper.tex
paper

\subsubsection{prose \cite{bepler2021learning}}
The model structure is a multi-layer bidirectional Long Short Term Memory (bi-LSTM). Following the intuition that some aspect of proteins structure and semantic can never be discoverable by statistical sequence models alone, they came up with the idea of multi-task learning with strictural supervision. The learning tasks are: 1) classical masked language modeling task, 2) residue-residue contact prediction, 3) structural similarity prediction. This model ouperformed existing approaches in both transmembrane position labeling and phenotypes prediction of sequence variants.

\subsubsection{alphafold}

@@

@@

\subsubsection{Evolutionary scale modeling}

\subsection{Combining the (contextual) representations}derived by concatenating the outputs of the three layers of ELMo, each describing a token with a vector of length 1024
We tried four methods to join togheter the amminoacid embeddings in order to produce a fixed size embedding for the chunk: average, maximum, sum and principal component analysis (PCA).

@@

\onecolumn
\begin{table}[htb]
\centering
\begin{tabular}{|l c c|} 
    \hline
    Name & input length (chunk) & embedding dimension  \\ 
    \hline
    embedding reproduction (rep)\cite{yang2018learned}       & 64    & 64 per chunk   \\
    seqvec \cite{heinzinger2019modeling} & 1024 & 1024 per amminoacid \\
    dnabert \cite{ji2021dnabert}                     & 512     & 768 per chunk \\
    prose   \cite{bepler2021learning}                   & 512   & 100 per amino acid   \\
    alphafold  \cite{jumper2021highly}                 & 1024   & 384 per ammino acid\\
    evolutionary scale modeling (esm2) \cite{lin2022language}   & 1024    & 1280 per ammino acid \\  
    \hline
\end{tabular}
\caption{Embedders used in the experiments, their maximum imput length and the dimension of the embedding produced.}
\label{tab:embedders}
\end{table}
\twocolumn

>>>>

\subsubsection{Prose \cite{bepler2021learning}}
The model structure is a multi-layer bidirectional Long Short Term Memory (bi-LSTM). Following the intuition that some aspect of proteins structure and semantic can never be discoverable by statistical sequence models alone, they came up with the idea of multi-task learning with strictural supervision. The learning tasks are: 1) classical masked language modeling task, 2) residue-residue contact prediction, 3) structural similarity prediction. This model ouperformed existing approaches in both transmembrane position labeling and phenotypes prediction of sequence variants.

\subsubsection{Alphafold}

- evoformer module and structure module. The Evoformer, builds separate MSA and residue-pairwise embedding spaces

@@

- used without the MSA and templates

@@

\subsubsection{Evolutionary scale modeling \cite{lin2023evolutionary}}
The underlying architecture is a BERT \cite{devlin2018bert} style encoder tarnsformer with modifications in the number of layers, number of attention heads, hidden size and feed forward hidden size. A further improvement is the use of Rotary Position Embedding \cite{su2021roformer} that allows to generalize beyond the context window it is trained on.
The main advantages compared to AlphaFold are the removal of the the need of multiple sequence alignment and an increasing up to two order of magnitude of  the speed of the prediction pipeline.
We used the version with 33 layers and 650B parameters (compare with alphafold)

\subsection{Combining the (contextual) representations}
We tried four methods to join togheter the amminoacid embeddings in order to produce a fixed size embedding for the chunk: average, maximum, sum and principal component analysis (PCA).

@@

\onecolumn
\begin{table}[htb]
\centering
\begin{tabular}{|l c c|} 
    \hline
    Name & input length (chunk) & embedding dimension  \\ 
    \hline
    embedding reproduction (rep)\cite{yang2018learned}       & 64    & 64 per chunk   \\
    seqvec \cite{heinzinger2019modeling} & 1024 & 1024 per amminoacid \\
    dnabert \cite{ji2021dnabert}                     & 512     & 768 per chunk \\
    prose   \cite{bepler2021learning}                   & 512   & 100 per amino acid   \\
    alphafold  \cite{jumper2021highly}                 & 1024   & 384 per ammino acid\\
    evolutionary scale modeling (esm2) \cite{lin2023evolutionary}   & 1024    & 1280 per ammino acid \\  
    \hline
\end{tabular}
\caption{Embedders used in the experiments, their maximum imput length and the dimension of the embedding produced.}
\label{tab:embedders}
\end{table}
\twocolumn
